In this chapter we look back at the thesis project and discuss how one can design for meaningful interactive experiences in a museum space.

\section{The nature of the contributions}
This thesis has two research contributions, one theoretical and one practical:
\begin{itemize}
    \item Theoretical contribution: framework used to identify and analyse dialogic relations between visitor and interactive installations.
    \item Practical contribution to HCI/ IxD field: dialogical installation patterns that objectify meaningfulness as a quality that you can design for.
\end{itemize}


The framework: A resource for the designer to judge the degree of dialogic instalaltion design, dialogic visitor experience and museum space hybridness. Together, they synthesise an understanding of meaningfulness rooted in the museum/ exhibition artefacts supporting or extending dialogic behaviour: conversations, reflections etc, between the visitor and installation. But also from visitor-to-visitor, or groups, walking through the museum narrative. This would be a good fit for museum disseminating discourses that demand/ wish to stimulate dialogue as one of the main "things" the visitor should "sitte igjen med" after the museum visit. I would argue this is relevant for museums disseminating contemporary discourses, like the climate crisis, to ensure partaking in the public debate. And help manifest the museum space as a modern place being able to "følge med i tiden".. 

We have shown how the framework can be applied to analyse a specific exhibition addressing one discourse. But also seen how the framework work across different installations and exhibitions addressing different discourses. Doing an analysis as such could prove useful for a city planning a new museum, seeing how the museums differ in terms of meaningfulness and stimulating dialogic behaviour. Perhaps new museums can fill, or complement, a gap that the existing museums does not. 

What is nice with the framework is that it is designed for interactive installations- and artefacts, but it allows for "analogue" artworks or artefacts parts of the exhibition to take part in the analysis as well. If the curator is looking at the exhibition as a whole, it would make sense to involve all parts of the journey. E.g., Klimahuset and ice cube. 

\section{Contributions to the field}

This thesis contribution is valuable for the broader HCI community interested in designing or analysing public installations in museums. By presenting a theoretical framework used to both identify and analyse dialogic relations between visitor and interactive installations. 

HCI is increasingly interested in considering how technology-use impacts the human experience of meaning \autocite{kaptelinin_technology_2018}, \autocite{light_design_2017}, as well as how to design for and foster meaningful user experiences \autocite{grosse-hering_slow_2013}, \autocite{Hassenzahl_Moments_2013}.


Literature concerned with interactivity and meaningful engagement with visitors [ \autocite{mccarthy_place}, \autocite{ciolfi_designing_2012}], are often written in the context of heritage museums. While this thesis contribution is derived in the context of different museum fictions; art (MUNCH), science (Teknisk Museum), and natural history (Klimahuset). 


Literature agrees on museums having become a place for education and learning, dialogue and debate \autocite{narrative_sitzia}, \autocite{hein_1998}, \autocite{hooper_1994}, \autocite{Roberts_1997}. An interest that is also shared politically, as evident in \autocite{melding23}. 

Surveys from, for example, the USA show that museums score higher on trust than other institutions, such as media and government agencies, and that credibility of museums continues to increase during the pandemic \autocite{impact_2020}. As important actors in the public discourse, it is crucial for museums in the future that they defend this position and further develop it. It is essential to secure a position where a room is created for different opinions to meet and break and counter the emergence of echo chambers, conspiracy theories, and false news \autocite[p. 41]{melding23}.


Then comes the question, what does the interactive artefact or installation represent? As far as my literature search goes, there is not so much attention given to the role of the interactive artefact or installation in the HCI community. The community seem to be more interested on what makes the installation engaging, and how it can provide an engaging experience for the visitor and groups as evident in the works of \autocite{hornecker_learning_2006}, and \autocite{ciolfi_designing_2012}.

"For the last several years the HCI community has been undergoing a broadening of scope from usability to user experience; making things that improve the quality of people’s lives across a range of contexts. Our community has recognized that in addition to making products that make people more efficient and effective, we need to learn to make things that affect people in a variety of ways." \autocite[p. 395]{zimmerman_designing_2009}. 

There has been increased interest in the field of visitor studies and museum research in the details of visitor behaviour in museums, which is what the research done on indexing contributes to \autocite[p. 41]{hornecker_to-and-fro_2016}


"Thanks to the development of ubiquitous and pervasive technologies, research focusing on the design of novel interactive artefacts has recently become more concerned with studying and understanding the spatial properties of the world" \autocite[p. 159]{hybridplace_ciolfi}

In Ciolfi and McCarthy’s opinion, frameworks that have been made to guide the design of interactive museum exhibitions developed in the field of museums studies, underplay aspects of visitor’s active sense making and interpretation. They argue that most practical and conceptual contributions from both museum studies and interaction design have fallen short of their potential to reflect on and design technologically mediated museum experiences partly because of the underdeveloped or under-articulated conceptualisations of visitor experience with which they work \autocite[p. 248]{mccarthy_place}


\textbf{USE OF PATTERNS:} "My use of design patterns deviates fairly widely from their intended purpose of documenting and making explicit design conventions. The design patterns from the individual products are not particularly valuable to other designers, because they do not document a general solution. However, they worked very well to illuminate the link between design intention (application of product design theory) and the designed artifact, allowing the similarities in the application of theory across the very different design projects to be seen." \autocite[p. 402]{zimmerman_designing_2009}.


\subsection{Generating knowledge through analysis of design}
As a field, HCI must answer what sorts of knowledge outcomes can come from objects in (art and) design projects; if we cant, we cannot legitimize RtD as a way of doing HCI research. Bardzell offer theoretical support for RtD by arguing that to legitimise and make use of research through design as \emph{research}, HCI researchers need to explore and clarify how RtD objects contribute to knowledge \autocite[p.2093]{bardzell_immodest_2015}. Along these lines, Bardzell et.al argue that while the \emph{intentions} of the object's designer are important and annotations are a good mechanism to articulate them, the critical reception of objects can be equally generative of RtD's knowledge impacts \autocite[p. 2093]{bardzell_immodest_2015}. Bardzell et.al. investigate RtD in its relation to the production of knowledge; specifically, \emph{how design objects are knowledge producers both for those that encounter them and those that design them} \autocite[p. 2093]{bardzell_immodest_2015}. To explore how a detailed critique might work when we understand objects as knowledge producers offering to the viewer the possibility to engage in meaning-making practises unfolding a range of complex and multi-faceted views, Bardzell et. al offer a multilevel analysis of a critical design fiction. \autocite[p. 2094]{bardzell_immodest_2015}.

The primary purpose of this thesis has been to contribute with knowledge that makes visible dialogic relations between interactive installations and visitor-experience in the museum space, to attempt to answer how one can design meaningful interactive experiences in a museum space. "By making different things intended to address the same problematic situation, RtD can reveal design patterns \autocite{Alexander_book} around problem framings, around specific interactions, and around how theory can be operationalized" \autocite[p. 178]{zimmerman_research_2014}.


\section{Disposition}

"Overall this paper contributes to HCI research on the technological augmentation of heritage sites both by addressing a seldom-studied domain, (...) This contribution is also of value for the broader HCI community interested in public installations, by showing how a thoughtful assembly of different interactional elements (from mobile applications, to standalone pieces and low-tech tangible components) can engage visitors and engender the establishment of personal connections." \autocite{ciolfi_designing_2012}


\begin{itemize}
    \item Contribution 1: by putting three theoretical approaches together we have made a framework (chapter 6) that proposes a new way of designing for meaningfulness. The new framework have been used to guide datagathering (chapter 8), and through analysis we have proven how we can derive a list of patterns. The framework have therefore proved useful as a tool for designers following a whole iteration in a design process.
    
    
    \item Contribution 2: the list of patterns. They can be used (by designers) in early conceptual stages as inspiration or starting points for dialogic installation designs. 
    \item These contributions is the answer to; \emph{How one can design for meaningful interactive experiences in a museum space.}
    \item
    
     \item These contributions + literature review (chapter 2), is the answer to; \emph{How can one (...) in a museum space that addresses \textbf{sustainability}}. Sustainability represents a contemporary discourse that demand active discussion and engagement. Dialogic installations are my proposal of a way that museums can address contemporary issues without being cultural moralists, simply facilitating for reflection, and dialogue in the museum, as the  in the time after the visit. 
    \item Discuss dialogic installation design up against the field's current "state" or contributions of something like that.

\end{itemize}


\section{Research as a creative, generative process (or something like this?)}
This study reflects the challenging "climate" where design research meet installation design, museums facilitating attitude change and sustainability as a contemporary, and complex (!), discourse.

At the time, I was unaware of the methodological and practical consequences of structuring my understanding through three different theories, while doing research through design. It has been a time-consuming effort to support this methodological choice and find support in the literature as to how this way of doing RtD has generated knowledge. 





\begin{itemize}
    \item Contributions to the field (HCI, interaction design, museum studies). HCI/ I.D. --> RtD as a generative and creative process. Museum studies: an attempt to objectify interactive meaningful qualities in museum spaces
    \item Discuss my term "meaningfulness" up against the field's definition of meaningfulness. 
    
    \item Documentation --> the researchers basis for contributions (\emph{the research}). In this study, the documentation have played a creative and generative role - just as much as being sound (valid) for scientific purposes like analysis. 
    \item RQ ---> in this study used as a "creative driver" for the design process. Seen as something "alive", fluid, that drives conceptual exploration just as much as the scientific exploration/ inquiry.
    \item Science is a generative and creative process. This study aim to strengthen the notion that design has a place in research, agreeing with Frayling and RtD literature saying that science + design = true. 

\end{itemize}


